GO

### 2019-12-15 analysis/12_GO.Rmd
merged GO and caididates

@@

```{r GO_DEGs}
GO_DEGs <- left_join(allGO, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>% 
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control.bldg"), contains("bldg.lay"), contains("lay.inc.d3"),
         contains("inc.d3.inc.d9"), contains("inc.d9.inc.d17"), contains("inc.d17.hatch"),
         contains("hatch.n5"), contains("n5.n9")) %>%
  filter(GO %in% c("endocrineprocess", "lactation", 
                   "parentalbehavior", "matingbehavior")) %>% 
  map(~.x) %>%
  discard(~all(is.na(.x))) %>%
  map_df(~.x)
```

@@

```{r}
candidates <- c("AVP", "PRL", "PRLR", "GNIH",  "OXT", "AVPR1A", "AVPR1B",
                "CRH", "FSHB", "GH", "GNRH1", "GNRH2",
                "MC4R", "JAK2", "HCRT", "POMC", "TRH", "TSHB",
                "LH", "FSH")
candidates <- as.data.frame(candidates)
names(candidates)[1] <- "gene"
candidates$GO <- "candidate genes"

>>>>

## add candidate genes

```{r}
candidates <- c(  "PRLR", 
                 "AVP", "VIP", "AVPR1A", "AVPR1B", "OXT", 
                 "GNRH1", "NPY",
                "CRH", "FSHB", "GH", 
                 "JAK2", "HCRT", "TRH", "TSHB",
                "LH", "FSH",
                "MC3R", "MC4R", "MC5R", 
                "ESR1", "ESR2", "AR", 
                "STAT5B", "CISH")
candidates <- as.data.frame(candidates)
names(candidates)[1] <- "gene"
candidates$GO <- "candidategenes"
candidates <- candidates %>% select(GO, gene)

allGO <- rbind(candidates, allGO)
head(allGO)
```

@@

```{r GO_DEGs}
GO_DEGs <- left_join(allGO, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>% 
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control.bldg"), contains("bldg.lay"), contains("lay.inc.d3"),
         contains("inc.d3.inc.d9"), contains("inc.d9.inc.d17"), contains("inc.d17.hatch"),
         contains("hatch.n5"), contains("n5.n9")) %>%
  filter(GO %in% c("endocrineprocess", "lactation", 
                   "parentalbehavior", "matingbehavior",
                   "candidategenes")) %>% 
  map(~.x) %>%
  discard(~all(is.na(.x))) %>%
  map_df(~.x)
```

@@

```{r}
candidates <- c( "PRL", "PRLR", 
                 "AVP", "VIP", "AVPR1A", "AVPR1B", "OXT", 
                 "GNRH1", "GNRHR", "NPY",
                "CRH", "FSHB", "GH", 
                 "JAK2", "HCRT", "POMC", "TRH", "TSHB",
                "LH", "FSH",
                "POMC", "MC3R", "MC4R", "MC5R", 
                "ESR1", "ESR2", "AR", 
                "STAT5", "CISH")
candidates <- as.data.frame(candidates)
names(candidates)[1] <- "gene"
candidates$GO <- "candidate genes"
